---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

## Economist Learning example

This is a code along to this amazing [recreation of the economist chart](https://www.blog.cultureofinsight.com/2017/07/recreating-an-economist-wdi-chart-in-r/?utm_content=buffera0719&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer).

### Setup

```{r setup, cache=TRUE, results='hide',warning=FALSE,message=FALSE}
pckgs <- c("tidyverse", "WDI", "gganimate")
# install.packages(pckgs)
# devtools::install_github("hrbrmstr/hrbrthemes")
library(tidyverse)
# install.packages('extrafont')
library(extrafont)
extrafont::font_import()
extrafont::loadfonts()
library(WDI)
library(hrbrthemes)
library(glue)
# library(gganimate)
```
Apparently `gganimate` is not available for R 3.5.0. It's ok, we'll
keep working on.

### Get the data

We first get the most up to date data from `WDI`
*NOTE:* Is this a way to refresh a data package without explicitly using
`update.packages`? Look into `WDIcache()` functionality.

We can search for the relevant dataset using `regex`. We appear to require
the `NY.GDP.MKTP.KD` dataset.

```{r src_date, cache=TRUE, echo=TRUE}
countries <- c("Liberia", "Ukraine", "Rwanda", "Indonesia", "Zimbabwe", "Greece")
countries_codes <- c("LR","UA", "RW", "ID", "ZW", "GR")
new_cache = WDI::WDIcache()
WDI::WDIsearch(string = "gdp.*constant.*2010", cache = new_cache)
dat <- WDI::WDI(indicator = 'NY.GDP.MKTP.KD', country = countries_codes,
                start = 1988, end = 2016, cache = new_cache)
```

### Wrangling the data

```{r wrangle_data_01, cache=TRUE}
years <- c(1988, 1989, 1992, 1997, 2001, 2007)

#' Create seperate df for each country with appropriate time periods
#  add GDP indexes and years since columns then store in a list
#'
#' @param dat 
#' @param x 
filt_cntry <- function(dat, x){
    out <- dat %>% 
                dplyr::filter(country == countries[x], 
                              year >= years[x]) %>% 
                dplyr::rename(GDP = NY.GDP.MKTP.KD) %>% 
                dplyr::mutate(index = GDP / (GDP[1] / 100),
                          years_since = row_number() -1,
                          country = factor(country, levels = countries))
    base::return(out)
}

final_dat <- purrr::map_df(.x = base::seq.int(from = 1, to = length(years),
                                              by = 1),
                           ~ filt_cntry(dat = dat, x = .x))

head(final_dat)
```

### Visualizing

```{r plot_01, cache=TRUE}
ggplot2::ggplot(data = final_dat, aes(x = years_since, y = index, 
                                      color = country)) +
    ggplot2::geom_hline(yintercept = 100, color = "red", linetype = 1) +
    ggplot2::geom_line(size = 1) +
    ggplot2::geom_point(aes(x = 0, y = 100), color = "black", size = 2) +
    ggplot2::scale_x_continuous(expand = c(0.02, 0)) +
    ggplot2::scale_color_brewer(palette = "Dark2",
                                labels = base::as.vector(glue::glue('{countries} ({years})'))) +
    ggplot2::labs(title = "Shock Therapy - Selected Economic Collapses Since 1988", 
       subtitle = "100 = GDP prior to collapse (in constant 2010 $)",
       y = "", x = "Years since collapse",
       caption = "Source: World Bank",
       color = "Country") +
    # theme_ipsum(base_family = "Iosevka", grid_col = "white") +
    ggplot2::theme(plot.background = element_rect(fill = "#cddee7"))
```


# Notes 

The `theme_ipsum` line commented is not working correctly. Come back and resolve this issue.

